Evaluating procedures for updating catch advice between stock assessments of reef fishes with management strategy evaluation

### 2022-03-16 RunMSE/SEFSC/Manuscript/MainText.tex
updated rds files

%%% Main document
% BEGIN DOCUMENT
\begin{document}
\SweaveOpts{concordance=TRUE}

<<setup, include=FALSE, cache=FALSE, echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figures/plots-', fig.align='center', fig.show='hold', eval=TRUE, echo=FALSE)
#options(replace.assign=TRUE,width=80)
Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
@

<<admin, echo=FALSE,warning=FALSE,message=FALSE>>=
#load("../.RData")
library(english) # For english() function which converts numbers to words
library(Hmisc)
library(stringr)
library(tinytex)
# tinytex::tlmgr_update()
# tinytex::reinstall_tinytex()
dir_figs <- "../Figs"
@

<<latexTable, echo=FALSE>>=

@

<<parsForText, echo=FALSE>>=
# my wrapper function for formatting numbers with commas separating thousands
tn <- function(x){
  prettyNum(x,big.mark=",",scientific=FALSE)
  }

# Update these later based on saved results
n_sp <- english(3)
n_scen <- 10
n_MP <- 13

@

@@

\begin{abstract}
We built operating models for \Sexpr{n_sp} reef fish species from the US Southeast Atlantic, based on recent stock assessments. We developed \Sexpr{n_scen} scenerios and \Sexpr{n_MP} management procedures. Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.

>>>>

%%% Main document
% BEGIN DOCUMENT
\usepackage{Sweave}
\begin{document}
\input{MainText-concordance}

@@

\begin{abstract}
We built operating models for three reef fish species from the US Southeast Atlantic, based on recent stock assessments. We developed 10 scenerios and 13 management procedures. Management procedures varied in terms of how often stock assessments were conducted, and how catch advice was adjusted between stock assessments.
